---
title: BPD additional analysis and viz
author: Tamas Nagy
date: 11/12/2021
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
library(tidyverse)
library(janitor)
library(skimr)
library(ggsignif)
library(afex)
library(jtools)
library(lmerTest)
library(sjPlot)

theme_set(theme_apa())
```

```{r}


variable_names <-
  tribble(~scale, ~name, 
    "group_affect", "Video valence group",
    "extr", "Extremity",
    "bpd", "BPD trait",
    "cesd", "Participant mood (negative)",
    "gen_impr", "General impression of the video",
    "panas_neg", "Negative evaluation of the character",
    "panas_pos", "Positive evaluation of the character"
  ) %>% 
  mutate(name = fct_inorder(name))

```


```{r}
bpd_raw <-read_csv2(here::here("Data/data_final_long_scales_181121.csv"))

bpd_wide <-
  bpd_raw %>% 
  select(session,
         Group_affect,
         EXTR,
         BPD,
         CESD.t1, CESD.t2, CESD.t3, CESD.t4, 
         PANAS_POS.t1, PANAS_POS.t2, PANAS_POS.t3, PANAS_POS.t4,
         PANAS_NEG.t1, PANAS_NEG.t2, PANAS_NEG.t3, PANAS_NEG.t4,
         GEN_IMPR.t1, GEN_IMPR.t2, GEN_IMPR.t3, GEN_IMPR.t4
         ) %>% 
  clean_names() %>% 
  mutate(group_affect = str_to_title(group_affect),
         bpd_group = cut_number(bpd, 
                                n = 3, 
                                labels = c("Low BPD trait",
                                           "Medium BPD trait",
                                           "High BPD trait"),
                                ordered_result = TRUE)
         )

bpd_wide %>% 
  ggplot() +
  aes(x = bpd, fill = bpd_group) +
  geom_histogram(alpha = .7, binwidth = 1) +
  labs(title = "BPD score cut into 3 paproximately equivalent sized groups")

bpd_long <- 
  bpd_wide %>% 
  pivot_longer(cesd_t1:gen_impr_t4,
               names_to = c("scale", "time"),
               names_pattern = "(.*)_t(.)") %>% 
  mutate(time = as.integer(time)) %>% 
  left_join(variable_names, by = "scale")

bpd_tidy <- 
  bpd_wide %>% 
  pivot_longer(cesd_t1:gen_impr_t4,
               names_to = c(".value", "time"),
               names_pattern = "(.*)_t(.)") %>% 
  mutate(time = as.integer(time),
         group_affect = fct_relevel(group_affect, "Neutral"))

```

# Create descriptive table
```{r}

new_hist <- function(x){
  inline_hist(x, n_bins = 10)
}

my_skim <- skim_with(numeric = sfl(hist = new_hist))

bpd_tidy %>% 
  my_skim(extr:bpd, cesd:gen_impr) %>% 
  left_join(variable_names, by = c("skim_variable" = "scale")) %>% 
  select(Variable = name,
         Mean = numeric.mean,
         SD = numeric.sd,
         Min = numeric.p0,
         Max = numeric.p100,
         Distribution = numeric.hist) %>% 
  performance::print_html() %>% 
  gt::tab_options(table_body.hlines.width = 0)
  

```


# Recreate Figure 2

```{r}
#TODO: add exact p values instead of *s
fig2_sig <-
  variable_names %>% 
  slice(4:7) %>% 
  left_join(
    tribble(~scale, ~y, ~xmin, ~xmax, ~label,
            "cesd", -.3, 1, 2, "*** ",
            "cesd", -.4, 1, 3, " *** ",
            "cesd", -.5, 1, 4, " ***",
            "cesd", -.6, 2, 3, "*",
            "cesd", -.7, 2, 4, "**",
            "gen_impr", .5, 1, 2, "***",
            "gen_impr", .6, 1, 3, " ***",
            "gen_impr", .7, 1, 4, "*** ",
            "panas_pos", -.3, 1, 2, "*** ",
            "panas_pos", -.4, 1, 3, " ***",
            "panas_pos", -.5, 1, 4, " *** ",
            "panas_pos", -.6, 2, 3, "*",
            "panas_pos", -.7, 2, 4, " * "),

        by = "scale"
  )

bpd_long %>% 
  group_by(scale) %>% 
  mutate(value = scale(value) %>% as.numeric()) %>% 
  ungroup() %>% 
  ggplot() +
  aes(x = time, y = value, color = group_affect) +
  stat_summary(fun = mean, 
               geom = "line", 
               size = 1.2,
               alpha = .8) +
  stat_summary(fun = mean, 
             geom = "point") +
  stat_summary(fun.data = mean_se, 
               geom = "errorbar", 
               width = .3) +
  facet_wrap(~name, nrow = 1) +
  geom_signif(data = fig2_sig,
              aes(xmin = xmin,
                  xmax = xmax,
                  y_position = y,
                  annotations = label),
              inherit.aes = FALSE, 
              tip_length = 0, 
              vjust = .5,
              manual = TRUE,
              alpha = .6, 
            textsize = 3) +
  labs(y = "Standarised mean value (SE)",
       x = "Measurement",
       color = "Video valence group") +
  theme_light() +
  theme(legend.position = "top")

```

# Recreate Table 2 as a figure

```{r}

table2_sig <-
  variable_names %>% 
  slice(5:7) %>% 
  left_join(
    tribble(~scale, ~y, ~xmin, ~xmax, ~label,
            "gen_impr", .4, 1, 2, "p < .001",
            "gen_impr", .6, 1, 3, "p = .021",
            "gen_impr", .5, 2, 3, "p < .001 ",
            "panas_neg", .7, 1, 2, "p < .001",
            "panas_neg", .8, 1, 3, "p < .001 ",
            "panas_neg", .6, 2, 3, " p < .001 ",
            "panas_pos", .4, 1, 2, "p = .278",
            "panas_pos", .6, 1, 3, "p < .001",
            "panas_pos", .5, 2, 3, "p < .001 "
            ),
        by = "scale"
  )

bpd_long %>% 
  filter(scale != "cesd", time == 1) %>% 
  group_by(scale) %>% 
  mutate(value = scale(value) %>% as.numeric()) %>% 
  ungroup() %>% 
  ggplot() +
  aes(x = group_affect, y = value, fill = group_affect) +
  stat_summary(fun = mean, 
               geom = "col", 
               alpha = .8, 
               show.legend = FALSE) +
  stat_summary(fun.data = mean_se,
               geom = "errorbar",
               width = .3,
               alpha = .3) +
  facet_wrap(~name) +
  geom_signif(data = table2_sig,
              aes(xmin = xmin,
                  xmax = xmax,
                  y_position = y,
                  annotations = label),
              inherit.aes = FALSE, 
              tip_length = .005,
              manual = TRUE,
              alpha = .6, 
              textsize = 3) +
  labs(y = "Standardized mean value (SE)",
       x = "Video valence group")
```

# Reviewer 2 requested figure

It would also be helpful to include a graph on the relationship between borderline characteristics and the extent of enhancement of negative recall bias. I believe that this is the primary finding in the study but it does not come out clearly to the reader. 

```{r}
# H4-5
bpd_long %>% 
  filter(scale != "cesd") %>% 
  group_by(scale) %>% 
  mutate(value = scale(value) %>% as.numeric()) %>% 
  ungroup() %>% 
  ggplot() +
  aes(x = time, y = value, color = bpd_group) +
  stat_summary(fun = mean, 
               geom = "line", 
               size = 1.3,
               alpha = .7) +
  stat_summary(fun = mean, 
               geom = "point", 
               size = 3,
               alpha = .7) +
  stat_summary(fun.data = mean_se, 
              geom = "errorbar",
              width = .1,
              alpha = .7) +
  facet_grid(group_affect~name, 
             scales = "free_y") +
  labs(x = "Measurement",
       y = "Standardised mean value (SE)") +
  theme(legend.position = "top"
        )

```


# Rerun ANOVA with interaction terms
```{r}
# H4-5
mod_neg <- 
  lmer(scale(panas_neg) ~ group_affect * time * scale(bpd) + (1|session),
      data = bpd_tidy)

mod_pos <- 
  lmer(scale(panas_pos) ~ group_affect * time * scale(bpd) + (1|session),
       data = bpd_tidy)

mod_gen <-
  lmer(scale(gen_impr) ~ group_affect * time * scale(bpd) + (1|session),
       data = bpd_tidy)

anova(mod_neg)


tab_model(mod_gen, mod_neg, mod_pos,
          show.se = TRUE,
          show.ci = FALSE,
          show.stat = TRUE,
          dv.labels = variable_names$name[5:7])

```

```{r}
# TODO: H6: rerun all models as lmers
# Rework Table 4 as std betas 
# Use FDR correction!



```

